Supplementary Material for Asymmetry paper

### 2020-07-24 Supplementary/Sup_mat.Rmd
Corrected figure caption
Updated sup mat

## Experiment 4: Probability Matching
```{r load data, include = F, echo = F, message = F, warning = F}
load("../power/Prob_match/scratch/df_resample")
```

@@

@@

```{r ProbExpAcc, include = T, echo = F, fig.asp = .45, fig.cap = "_These show the expected accuracy for each participant (black lines) plotted against $\\Delta$. The different shaded regions show the minimum (blue) and maximum (red) expected accuracy rates for all participants. $\\Delta$ is the separations at which each participant was tested rescaled to be between 0 and 1_"}
plt_prop_expAcc <- readPNG("../Figures/Experiment_4_Prob/region_performance.png")
grid.raster(plt_prop_expAcc)
```

>>>>

@@

### Power Analysis
```{r load data, include = F, echo = F, message = F, warning = F}
load("../power/Prob_match/scratch/df_resample")
```

@@

```{r ProbExpAcc, include = T, echo = F, fig.asp = .45, fig.cap = "_These show the expected accuracy for each participant (black lines) plotted against $\\Delta$. The different shaded regions show the minimum (orange) and maximum (green) expected accuracy rates for all participants. $\\Delta$ is the separations at which each participant was tested rescaled to be between 0 and 1_"}
plt_prop_expAcc <- readPNG("../Figures/Experiment_4_Prob/region_performance.png")
grid.raster(plt_prop_expAcc)
```
